Articles of Association of London Hackspace Ltd

### 2012-09-30 constitution/articles-body.tex
Less/fewer
Change this to three to be consistent with the minimum number of directors.
Update to remove charity reference.
* Replace all refs to "charity" with "association".
* Remove references to the Charities Act.
* Remove extensive and complex "connected persons" wording.

\title{Articles of Association of London Hackspace Ltd.}
\begin{enumerate}
\item
  The company's name is London Hackspace Ltd. (and in this document
  it is called the ``charity'').

\section{Interpretation}

\item
  In the articles:
  \begin{description}
  \item[Address] means a postal address or, for the purposes of
    electronic communication, a fax number, an e-mail or postal address
    or a telephone number for receiving text messages in each case
    registered with the charity
  \item[The Articles] means these articles of association
  \item[Clear days] in relation to the period of a notice means a period
    excluding:
    \begin{itemize}
    \item
      the day when the notice is given or deemed to be given; and
    \item
      the day for which it is given or on which it is to take effect
    \end{itemize}
  \item[The Commission] means the Charity Commission for England and Wales
  \item[Companies Acts] means the Companies Acts (as defined in section
    2 of the Companies Act 2006) insofar as they apply to the charity
  \item[The Directors] means the directors of the charity. The directors
    are charity trustees as defined by section 97 of the Charities Act
    1993
  \item[Document] includes, unless otherwise specified, any document
    sent or supplied in electronic form
  \item[Electronic Form] has the meaning given in section 1168 of the Companies Act 2006
  \item[Officers] includes the directors and the secretary (if any)
  \item[Secretary] means any person appointed to perform the duties of
    the secretary of the charity
  \end{description}
  Words importing one gender shall include all genders, and the singular
  includes the plural and vice versa.

  Unless the context otherwise requires words or expressions
  contained in the articles have the same meaning as in the Companies
  Acts but excluding any statutory modification not in force when
  this constitution becomes binding on the charity.

@@

\item
  The liability of the members is limited to a sum not exceeding £1,
  being the amount that each member undertakes to contribute to the
  assets of the charity in the event of its being wound up while he,
  she or it is a member or within one year after he, she or it ceases
  to be a member, for:
  \begin{enumerate}
  \item
    payment of the charity's debts and liabilities incurred before he,
    she or it ceases to be a member;
  \item
    payment of the costs, charges and expenses of winding up; and
  \item
    adjustment of the rights of the contributories among themselves.
  \end{enumerate}

@@

\item
  The charity's objects (``Objects'') are specifically restricted to
  the following:
  \begin{enumerate}
  \item
    to promote and encourage technical, scientific, and artistic skills through social collaboration and education; and
  \item
    to provide and maintain shared community workspace and equipment in London.
  \end{enumerate}

@@

\item
  The charity has power to do anything which is calculated to further
  its Objects or is conducive or incidental to doing so. In
  particular, the charity has power:
  \begin{enumerate}
  \item
    to raise funds. In doing so, the charity must not undertake any
    taxable permanent trading activity and must comply with any
    relevant statutory regulations;
  \item
    to buy, take on lease or in exchange, hire or otherwise acquire any
    property and to maintain and equip it for use;
  \item
    to sell, lease or otherwise dispose of all or any part of the
    property belonging to the charity. In exercising this power, the
    charity must comply as appropriate with sections 36 and 37 of the
    Charities Act 1993, as amended by the Charities Act 2006;
  \item
    to borrow money and to charge the whole or any part of the property
    belonging to the charity as security for repayment of the money
    borrowed or as security for a grant or the discharge of an
    obligation. The charity must comply as appropriate with sections 38
    and 39 of the Charities Act 1993, as amended by the Charities Act
    2006, if it wishes to mortgage land;
  \item
    to co-operate with other charities, voluntary bodies and statutory
    authorities and to exchange information and advice with them;
  \item
    to establish or support any charitable trusts, associations or
    institutions formed for any of the charitable purposes included in
    the Objects;
  \item
    to acquire, merge with or to enter into any partnership or joint
    venture arrangement with any other charity;
  \item
    to set aside income as a reserve against future expenditure but
    only in accordance with a written policy about reserves;
  \item
    to employ and remunerate such staff as are necessary for carrying
    out the work of the charity. The charity may employ or remunerate a
    director only to the extent it is permitted to do so by article \ref{cls:income-property}
    and provided it complies with the conditions in that article;
  \item
    to:
    \begin{enumerate}
    \item
      deposit or invest funds;
    \item
      employ a professional fund-manager; and
    \item
      arrange for the investments or other property of the charity to be
      held in the name of a nominee; in the same manner and subject to
      the same conditions as the trustees of a trust are permitted to do
      by the Trustee Act 2000;
    \end{enumerate}
  \item
    to provide indemnity insurance for the directors in accordance
    with, and subject to the conditions in, section 73F of the
    Charities Act 1993;
  \item
    to pay out of the funds of the charity the costs of forming and
    registering the charity both as a company and as a charity;
  \end{enumerate}

@@

\item
  \label{cls:income-property}
  \begin{enumerate}
  \item
    The income and property of the charity shall be applied solely
    towards the promotion of the Objects.
  \item
    \label{scls:director-reimburse}
    \begin{enumerate}
    \item
      A director is entitled to be reimbursed from the property of the
      charity or may pay out of such property reasonable expenses
      properly incurred by him or her when acting on behalf of the
      charity.
    \item
      A director may benefit from trustee indemnity insurance cover
      purchased at the charity's expense in accordance with, and subject
      to the conditions in, section 73F of the Charities Act 1993.
    \item
      A director may receive an indemnity from the charity in the
      circumstances specified in article \ref{cls:directors-indemnity}.
    \end{enumerate}
  \item
    None of the income or property of the charity may be paid or
    transferred directly or indirectly by way of dividend bonus or
    otherwise by way of profit to any member of the charity. This does
    not prevent a member who is not also a director receiving:
    \begin{enumerate}
    \item
      a benefit from the charity in the capacity of a beneficiary of the
      charity;
    \item
      reasonable and proper remuneration for any goods or services
      supplied to the charity.
    \end{enumerate}
  \item
    \label{scls:directors-remuneration} No director or connected person
    may:
    \begin{enumerate}
    \item
      buy any goods or services from the charity on terms preferential to
      those applicable to members of the public;
    \item
      sell goods, services, or any interest in land to the charity;
    \item
      be employed by, or receive any remuneration from, the charity;
    \item
      receive any other financial benefit from the charity; unless:
      \begin{enumerate}
      \item
        the payment is permitted by article \ref{scls:directors-scope}; or
      \item
        the directors obtain the prior written approval of the Commission
        and fully comply with any procedures it prescribes. In this article
        a `financial benefit' means a benefit, direct or indirect, which is
        either money or has a monetary value.
      \end{enumerate}
    \end{enumerate}
  \item
    \label{scls:directors-scope}
    \begin{enumerate}
    \item
      A director or connected person may receive a benefit from the
      charity as a beneficiary provided it is available generally to the
      beneficiaries of the charity.
    \item
      A director or connected person may enter into a contract for the
      supply of services, or of goods that are supplied in connection
      with the provision of services, to the charity where that is
      permitted in accordance with, and subject to the conditions in
      section 73A to 73C of the Charities Act 1993.
    \item
      Subject to article \ref{scls:supply-goods} a director or connected
      person may provide the charity with goods that are not supplied in
      connection with services provided to the charity by the director or
      connected person. \label{art:directors-goods}
    \item
      A director or connected person may receive interest on money lent
      to the charity at a reasonable and proper rate which must be 2\%
      (or more) per annum below the base rate of a clearing bank to be
      selected by the directors.
    \item
      A director or connected person may receive rent for premises let by
      the director or connected person to the charity if the amount of
      the rent and the other terms of the lease are reasonable and proper
      and provided that the director concerned shall withdraw from any
      meeting at which such a proposal or the rent or other terms of the
      lease are under discussion.
    \item
      The directors may arrange for the purchase, out of the funds of the
      charity, of insurance designed to indemnify the directors in
      accordance with the terms of, and subject to the conditions in,
      section 73F of the Charities Act 1993.
    \end{enumerate}
  \item \label{goods}
    \label{scls:supply-goods} The charity and its directors may only
    rely upon the authority provided by article
    \ref{art:directors-goods} if each of the following conditions is
    satisfied:
    \begin{enumerate}
    \item
      The amount or maximum amount of the payment for the goods is set
      out in an agreement in writing between:
      \begin{enumerate}
      \item
        the charity or its directors (as the case may be); and
      \item
        the director or connected person supplying the goods
        (``the supplier'') under which the supplier is to supply the goods
        in question to or on behalf of the charity.
      \end{enumerate}
    \item
      The amount or maximum amount of the payment for the goods does not
      exceed what is reasonable in the circumstances for the supply of
      the goods in question.
    \item
      The other directors are satisfied that it is in the best interests
      of the charity to contract with the supplier rather than with
      someone who is not a director or connected person. In reaching that
      decision the directors must balance the advantage of contracting
      with a director or connected person against the disadvantages of
      doing so.
    \item
      The supplier is absent from the part of any meeting at which there
      is discussion of the proposal to enter into a contract or
      arrangement with him or her or it with regard to the supply of
      goods to the charity.
    \item
      The supplier does not vote on any such matter and is not to be
      counted when calculating whether a quorum of directors is present
      at the meeting.
    \item
      The reason for their decision is recorded by the directors in the
      minute book.
    \item
      A majority of the directors then in office are not in receipt of
      remuneration or payments authorised by article
      \ref{scls:directors-remuneration}.
    \end{enumerate}
  \item \label{def-charity}
    In sub-clauses \ref{scls:director-reimburse} to \ref{goods}, ``charity'' shall include
    any company in which the charity:
    \begin{itemize}
    \item
      holds more than 50\% of the shares; or
    \item
      controls more than 50\% of the voting rights attached to the
      shares; or
    \item
      has the right to appoint one or more directors to the board of the
      company;
    \end{itemize}
  \item \label{def-connected}
    In sub-clauses \ref{scls:directors-remuneration} to \ref{goods}, \ref{conflict-interest-loyalty},
    and \ref{directors-validity-void} ``connected person'' means:
    \begin{enumerate}
    \item
      \label{art:connected-child} a child, parent, grandchild,
      grandparent, brother or sister of the director;
    \item
      \label{art:connected-spouse} the spouse or civil partner of the
      director or of any person falling within paragraph (i) above;
    \item
      \label{art:connected-business} a person carrying on business in
      partnership with the director or with any person falling within
      paragraph (i) or (ii) above;
    \item
      an institution which is controlled –
      \begin{enumerate}
      \item
        by the director or any connected person falling within paragraph (i) to (iii) above; or
      \item
        by two or more persons falling within sub-paragraph (A), when taken
        together
      \end{enumerate}
    \item
      a body corporate in which –
      \begin{enumerate}
        \item
            the director or any connected person falling within paragraphs (i) to (iii) has a substantial interest; or
        \item
            two or more persons falling within sub-paragraph (A) who, when
            taken together, have a substantial interest.
      \end{enumerate}
    \end{enumerate}
  \item
    For the purposes of interpreting the terms used in sub-clauses \ref{def-charity}
    and \ref{def-connected}, paragraphs 2 to 4 of Schedule 5 to the Charities Act 1993
    apply.
  \end{enumerate}

@@

\item
  \label{cls:subscribers}
  \begin{enumerate}
  \item
    The subscribers to the memorandum are the first members of the
    charity.
  \item
    Membership is open to other individuals or organisations who:
    \begin{enumerate}
    \item
      apply to the charity in the form required by the directors; and
    \item
      are approved by the directors.
    \end{enumerate}
  \item

    \begin{enumerate}
    \item
      The directors may only refuse an application for membership if,
      acting reasonably and properly, they consider it to be in the best
      interests of the charity to refuse the application.
    \item
      The directors must inform the applicant in writing of the reasons
      for the refusal within twenty-one days of the decision.
    \item
      The directors must consider any written representations the
      applicant may make about the decision. The directors' decision
      following any written representations must be notified to the
      applicant in writing but shall be final.
    \end{enumerate}
  \item
    Membership is not transferable.
  \item
    The directors must keep a register of names and addresses of the
    members.
  \end{enumerate}

@@

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies or, if it is an organisation, ceases to exist;
  \item
    the member resigns by written notice to the charity unless, after
    the resignation, there would be less than two members;
  \item
    any sum due from the member to the charity is not paid in full
    within two weeks of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the charity that his
    or her or its membership is terminated. A resolution to remove a
    member from membership may only be passed if:
    \begin{enumerate}
    \item
      the member has been given at least twenty-one days' notice in
      writing of the meeting of the directors at which the resolution
      will be proposed and the reasons why it is to be proposed;
    \item
      the member or, at the option of the member, the member's
      representative (who need not be a member of the charity) has been
      allowed to make representations to the meeting.
    \end{enumerate}
  \end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    The minimum periods of notice required to hold a general meeting of
    the charity are:
    \begin{enumerate}
    \item
      twenty-one clear days for an annual general meeting or a general
      meeting called for the passing of a special resolution;
    \item
      fourteen clear days for all other general meetings.
    \end{enumerate}
  \item
    A general meeting may be called by shorter notice if it is so
    agreed by a majority in number of members having a right to attend
    and vote at the meeting, being a majority who together hold not
    less than 90 percent of the total voting rights.
  \item
    The notice must specify the date time and place of the meeting and
    the general nature of the business to be transacted. If the meeting
    is to be an annual general meeting, the notice must say so. The
    notice must also contain a statement setting out the right of
    members to appoint a proxy under section 324 of the Companies Act
    2006 and article \ref{proxies}.
  \item
    The notice must be given to all the members and to the directors
    and auditors.
  \end{enumerate}

\item
  The proceedings at a meeting shall not be invalidated because a
  person who was entitled to receive notice of the meeting did not
  receive it because of an accidental omission by the charity.

@@

    \begin{enumerate}
    \item
      The declaration by the person who is chairing the meeting of the
      result of a vote shall be conclusive unless a poll is demanded.
    \item
      The result of the vote must be recorded in the minutes of the
      charity but the number or proportion of votes cast need not be
      recorded.
    \end{enumerate}
  \item

@@

\item \label{proxies}
  \begin{enumerate}
  \item
    Proxies may only validly be appointed by a notice in writing (a
    ``proxy notice'') which -
    \begin{enumerate}
    \item
      states the name and address of the member appointing the proxy;
    \item
      identifies the person appointed to be that member's proxy and the
      general meeting in relation to which that person is appointed;
    \item
      is signed by or on behalf of the member appointing the proxy, or is
      authenticated in such manner as the directors may determine; and
    \item
      is delivered to the charity in accordance with the articles and any
      instructions contained in the notice of the general meeting to
      which they relate.
    \end{enumerate}
  \item
    The charity may require proxy notices to be delivered in a
    particular form, and may specify different forms for different
    purposes.
  \item
    Proxy notices may specify how the proxy appointed under them is to
    vote (or that the proxy is to abstain from voting) on one or more
    resolutions.
  \item
    Unless a proxy notice indicates otherwise, it must be treated as -
    \begin{enumerate}
    \item
      allowing the person appointed under it as a proxy discretion as to
      how to vote on any ancillary or procedural resolutions put to the
      meeting; and
    \item
      appointing that person as a proxy in relation to any adjournment of
      the general meeting to which it relates as well as the meeting
      itself.
    \end{enumerate}
  \end{enumerate}

@@

\item
    \begin{enumerate}
        \item
        A person who is entitled to attend, speak or vote
        (either on a show of hands or on a poll) at a general meeting
        remains so entitled in respect of that meeting or any adjournment
        of it, even though a valid proxy notice has been delivered to the
        charity by or on behalf of that person.
        \item
        An appointment under a
        proxy notice may be revoked by delivering to the charity a notice
        in writing given by or on behalf of the person by whom or on whose
        behalf the proxy notice was given. 
        \item
        A notice revoking a proxy
        appointment only takes effect if it is delivered before the start
        of the meeting or adjourned meeting to which it relates 
        \item
        If a
        proxy notice is not executed by the person appointing the proxy, it
        must be accompanied by written evidence of the authority of the
        person who executed it to execute it on the appointor's behalf.
    \end{enumerate}

@@

\item
  Any objection to the qualification of any voter must be raised at
  the meeting at which the vote is tendered and the decision of the
  person who is chairing the meeting shall be final.
\item
  \begin{enumerate}
  \item
    Any organisation that is a member of the charity may nominate any
    person to act as its representative at any meeting of the charity.
  \item
    The organisation must give written notice to the charity of the
    name of its representative. The representative shall not be
    entitled to represent the organisation at any meeting unless the
    notice has been received by the charity. The representative may
    continue to represent the organisation until written notice to the
    contrary is received by the charity.
  \item
    Any notice given to the charity will be conclusive evidence that
    the representative is entitled to represent the organisation or
    that his or her authority has been revoked. The charity shall not
    be required to consider whether the representative has been
    properly appointed by the organisation.
  \end{enumerate}

@@

\item
  \begin{enumerate}
    A director must be a natural person aged 16 years or older.
  \item
    No one may be appointed a director if he or she would be
    disqualified from acting under the provisions of article \ref{director-cease}.
  \end{enumerate}
\item
  The number of directors shall be not less than three, nor more than eight.

\item
  The first directors shall be those persons notified to Companies
  House as the first directors of the charity.

\item
  A director may not appoint an alternate director or anyone to act
  on his or her behalf at meetings of the directors.

@@

\item
  \begin{enumerate}
  \item
    The directors shall manage the business of the charity and may
    exercise all the powers of the charity unless they are subject to
    any restrictions imposed by the Companies Acts, the articles or any
    special resolution.
  \item
    No alteration of the articles or any special resolution shall have
    retrospective effect to invalidate any prior act of the directors.
  \item
    Any meeting of directors at which a quorum is present at the time
    the relevant decision is made may exercise all the powers
    exercisable by the directors.
  \end{enumerate}

@@

\item
  The charity may by ordinary resolution:
  \begin{enumerate}
  \item
    appoint a person who is willing to act to be a director; and
  \item
    determine the rotation in which any additional directors are to
    retire.
  \end{enumerate}

\item
  No person other than a director retiring by rotation may be
  appointed a director at any general meeting unless:
  \begin{enumerate}
  \item
    he or she is recommended for re-election by the directors; or
  \item
    not less than fourteen nor more than thirty-five clear days before
    the date of the meeting, the charity is given a notice that:
    \begin{enumerate}
    \item
      is signed by a member entitled to vote at the meeting;
    \item
      states the member's intention to propose the appointment of a
      person as a director;
    \item
      contains the details that, if the person were to be appointed, the
      charity would have to file at Companies House; and
    \item
      is signed by the person who is to be proposed to show his or her
      willingness to be appointed.
    \end{enumerate}
  \end{enumerate}
\item
  All members who are entitled to receive notice of a general meeting
  must be given not less than seven nor more than twenty-eight clear
  days' notice of any resolution to be put to the meeting to appoint
  a director other than a director who is to retire by rotation.

\item
  \begin{enumerate}
  \item
    The directors may appoint a person who is willing to act to be a
    director.
  \item
    A director appointed by a resolution of the other directors must
    retire at the next annual general meeting and must not be taken
    into account in determining the directors who are to retire by
    rotation.
  \end{enumerate}
\item
  The appointment of a director, whether by the charity in general
  meeting or by the other directors, must not cause the number of
  directors to exceed any number fixed as the maximum number of
  directors.

@@

\item \label{director-cease}
  A director shall cease to hold office if he or she:
  \begin{enumerate}
    \item
    ceases to be a director by virtue of any provision in the
    Companies Acts or is prohibited by law from being a director; 
    \item
    is disqualified from acting as a trustee by virtue of section 72 of
    the Charities Act 1993 (or any statutory re-enactment or
    modification of that provision);
    \item
    ceases to be a member of the charity; 
    \item
    becomes incapable by reason of mental disorder, illness
    or injury of managing and administering his or her own affairs;
    \item 
    resigns as a director by notice to the charity (but only if at
    least two directors will remain in office when the notice of
    resignation is to take effect); or 
    \item 
    is absent without the
    permission of the directors from all their meetings held within a
    period of six consecutive months and the directors resolve that his
    or her office be vacated.
  \end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    The directors may delegate any of their powers or functions to a
    committee of two or more directors but the terms of any delegation
    must be recorded in the minute book.
  \item
    The directors may impose conditions when delegating, including the
    conditions that:
    \begin{enumerate}
    \item
      the relevant powers are to be exercised exclusively by the
      committee to whom they delegate;
    \item
      no expenditure may be incurred on behalf of the charity except in
      accordance with a budget previously agreed with the directors.
    \end{enumerate}
  \item
    The directors may revoke or alter a delegation.
  \item
    All acts and proceedings of any committees must be fully and
    promptly reported to the directors.
  \end{enumerate}

@@

\item \label{directors-interests}
  A director must declare the nature and extent of any interest,
  direct or indirect, which he or she has in a proposed transaction
  or arrangement with the charity or in any transaction or
  arrangement entered into by the charity which has not previously
  been declared. A director must absent himself or herself from any
  discussions of the directors in which it is possible that a
  conflict will arise between his or her duty to act solely in the
      interests of the charity and any personal interest (including but
  not limited to any personal financial interest).

@@

\item
The directors must keep minutes of all:
    \begin{enumerate}
        \item
            appointments of officers made by the directors;
        \item
            proceedings at meetings of the charity;
        \item
            meetings of the directors and committees of directors including:
            \begin{enumerate}
                \item
                    the names of the directors present at the meeting;
                \item
                    the decisions made at the meetings; and
                \item
                    where appropriate the reasons for the decisions.
            \end{enumerate}
    \end{enumerate}

>>>>

\title{Articles of Association of London Hackspace Ltd}
\begin{enumerate}
\section{Interpretation}
\item
  In the articles:
  \begin{description}
  \item[the association] the above-named association.
  \item[Address] means a postal address or, for the purposes of
    electronic communication, a fax number, an e-mail or postal address
    or a telephone number for receiving text messages in each case
    registered with the association
  \item[The Articles] means these articles of association
  \item[Clear days] in relation to the period of a notice means a period
    excluding:
    \begin{itemize}
    \item
      the day when the notice is given or deemed to be given; and
    \item
      the day for which it is given or on which it is to take effect
    \end{itemize}
  \item[Companies Acts] means the Companies Acts (as defined in section
    2 of the Companies Act 2006) insofar as they apply to the association
  \item[The Directors] means the directors of the association.
  \item[Document] includes, unless otherwise specified, any document sent or supplied in electronic form
  \item[Electronic Form] has the meaning given in section 1168 of the Companies Act 2006
  \item[Officers] includes the directors and the secretary (if any)
  \item[Secretary] means any person appointed to perform the duties of
    the secretary of the association.
  \end{description}
  Words importing one gender shall include all genders, and the singular
  includes the plural and vice versa.

  Unless the context otherwise requires, words or expressions
  contained in the articles have the same meaning as in the Companies
  Acts as in force on the date when these Articles become binding
  on the association.

@@

\item
  The liability of the members is limited to £1, being the amount that
  each member undertakes to contribute to the assets of the association
  in the event of its being wound up while he, she or it is a member or
  within one year after he, she or it ceases to be a member, for:
  \begin{enumerate}
  \item
    payment of the association's debts and liabilities incurred before he,
    she or it ceases to be a member;
  \item
    payment of the costs, charges and expenses of winding up; and
  \item
    adjustment of the rights of the contributories among themselves.
  \end{enumerate}

@@

\item
  The objects of the association are:
  \begin{enumerate}
  \item
    to promote and encourage technical, scientific, and artistic skills through social collaboration and education; and
  \item
    to provide and maintain shared community workspace and equipment in Greater London.
  \end{enumerate}

@@

\item
  The association has power to do anything which is calculated to further
  its Objects or is conducive or incidental to doing so. In
  particular, the association has power:
  \begin{enumerate}
  \item
    to raise funds. 
  \item
    to buy, take on lease or in exchange, hire or otherwise acquire any
    property and to maintain and equip it for use;
  \item
    to sell, lease or otherwise dispose of all or any part of the
    property belonging to the association.  
  \item
    to borrow money and to charge the whole or any part of the property
    belonging to the association as security for repayment of the money
    borrowed or as security for a grant or the discharge of an
    obligation.
  \item
    to acquire, merge with or to enter into any partnership or joint
    venture arrangement with any other association;
  \item
    to set aside income as a reserve against future expenditure but
    only in accordance with a written policy about reserves;
  \item
    to employ and remunerate such staff as are necessary for carrying
    out the work of the association. The association may employ or remunerate a
    director only to the extent it is permitted to do so by article \ref{cls:income-property}
    and provided it complies with the conditions in that article;
  \item
    to:
    \begin{enumerate}
    \item
      deposit or invest funds; and
    \item
      employ a professional fund-manager.
    \end{enumerate}
  \item
    to provide indemnity insurance for the directors.
  \item
    to pay out of the funds of the association the costs of forming and
    registering the association;
  \end{enumerate}

@@

\item
  \label{cls:income-property}
  \begin{enumerate}
  \item
    The income and property of the association shall be applied solely
    towards the promotion of the Objects.
  \item
    \label{scls:director-reimburse}
    \begin{enumerate}
    \item
      A director is entitled to be reimbursed from the property of the
      association or may pay out of such property reasonable expenses
      properly incurred by him or her when acting on behalf of the
      association.
    \item
      A director may receive an indemnity from the association in the
      circumstances specified in article \ref{cls:directors-indemnity}.
    \end{enumerate}
  \item
    None of the income or property of the association may be paid or transferred,
    directly or indirectly, by way of dividend, bonus, or otherwise by way of
    profit to any member of the association. This does not prevent a member who
    is not also a director receiving:
    \begin{enumerate}
    \item
      a benefit from the association in the capacity of a beneficiary of the
      association;
    \item
      reasonable and proper remuneration for any goods or services
      supplied to the association.
    \end{enumerate}
  \end{enumerate}

@@

\item
  \label{cls:subscribers}
  \begin{enumerate}
  \item
    The subscribers to the memorandum are the first members of the association.
  \item
    Membership is open to other individuals or organisations who:
    \begin{enumerate}
    \item
      apply to the association in the form required by the directors; and
    \item
      are approved by the directors.
    \end{enumerate}
  \item

    \begin{enumerate}
    \item
      The directors may only refuse an application for membership if,
      acting reasonably and properly, they consider it to be in the best
      interests of the association to refuse the application.
    \item
      The directors must inform the applicant in writing of the reasons
      for the refusal within twenty-one days of the decision.
    \item
      The directors must consider any written representations the
      applicant may make about the decision. The directors' decision
      following any written representations must be notified to the
      applicant in writing but shall be final.
    \end{enumerate}
  \item
    Membership is not transferable.
  \item
    The directors must keep a register of names and addresses of the
    members.
  \end{enumerate}

@@

\item
  Membership is terminated if:
  \begin{enumerate}
  \item
    the member dies or, if it is an organisation, ceases to exist;
  \item
    the member resigns by written notice to the association unless, after
    the resignation, there would be fewer than three members;
  \item
    any sum due from the member to the association is not paid in full
    within two weeks of it falling due;
  \item
    the member is removed from membership by a resolution of the
    directors that it is in the best interests of the association that his
    or her or its membership is terminated. A resolution to remove a
    member from membership may only be passed if:
    \begin{enumerate}
    \item
      the member has been given at least twenty-one days' notice in
      writing of the meeting of the directors at which the resolution
      will be proposed and the reasons why it is to be proposed;
    \item
      the member or, at the option of the member, the member's
      representative (who need not be a member of the association) has been
      allowed to make representations to the meeting.
    \end{enumerate}
  \end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    The minimum periods of notice required to hold a general meeting of
    the association are:
    \begin{enumerate}
    \item
      twenty-one clear days for an annual general meeting or a general
      meeting called for the passing of a special resolution;
    \item
      fourteen clear days for all other general meetings.
    \end{enumerate}
  \item
    A general meeting may be called by shorter notice if it is so
    agreed by a majority in number of members having a right to attend
    and vote at the meeting, being a majority who together hold not
    less than 90 percent of the total voting rights.
  \item
    The notice must specify the date time and place of the meeting and
    the general nature of the business to be transacted. If the meeting
    is to be an annual general meeting, the notice must say so. The
    notice must also contain a statement setting out the right of
    members to appoint a proxy under section 324 of the Companies Act
    2006 and article \ref{proxies}.
  \item
    The notice must be given to all the members and to the directors
    and auditors.
  \end{enumerate}

\item
  The proceedings at a meeting shall not be invalidated because a
  person who was entitled to receive notice of the meeting did not
  receive it because of an accidental omission by the association.

@@

    \begin{enumerate}
    \item
      The declaration by the person who is chairing the meeting of the
      result of a vote shall be conclusive unless a poll is demanded.
    \item
      The result of the vote must be recorded in the minutes of the
      association but the number or proportion of votes cast need not be
      recorded.
    \end{enumerate}
  \item

@@

\item \label{proxies}
  \begin{enumerate}
  \item
    Proxies may only validly be appointed by a notice in writing (a
    ``proxy notice'') which -
    \begin{enumerate}
    \item
      states the name and address of the member appointing the proxy;
    \item
      identifies the person appointed to be that member's proxy and the
      general meeting in relation to which that person is appointed;
    \item
      is signed by or on behalf of the member appointing the proxy, or is
      authenticated in such manner as the directors may determine; and
    \item
      is delivered to the association in accordance with the articles and any
      instructions contained in the notice of the general meeting to
      which they relate.
    \end{enumerate}
  \item
    The association may require proxy notices to be delivered in a
    particular form, and may specify different forms for different
    purposes.
  \item
    Proxy notices may specify how the proxy appointed under them is to
    vote (or that the proxy is to abstain from voting) on one or more
    resolutions.
  \item
    Unless a proxy notice indicates otherwise, it must be treated as -
    \begin{enumerate}
    \item
      allowing the person appointed under it as a proxy discretion as to
      how to vote on any ancillary or procedural resolutions put to the
      meeting; and
    \item
      appointing that person as a proxy in relation to any adjournment of
      the general meeting to which it relates as well as the meeting
      itself.
    \end{enumerate}
  \end{enumerate}

@@

\item
    \begin{enumerate}
        \item
        A person who is entitled to attend, speak or vote
        (either on a show of hands or on a poll) at a general meeting
        remains so entitled in respect of that meeting or any adjournment
        of it, even though a valid proxy notice has been delivered to the
        association by or on behalf of that person.
        \item
        An appointment under a
        proxy notice may be revoked by delivering to the association a notice
        in writing given by or on behalf of the person by whom or on whose
        behalf the proxy notice was given. 
        \item
        A notice revoking a proxy
        appointment only takes effect if it is delivered before the start
        of the meeting or adjourned meeting to which it relates 
        \item
        If a
        proxy notice is not executed by the person appointing the proxy, it
        must be accompanied by written evidence of the authority of the
        person who executed it to execute it on the appointor's behalf.
    \end{enumerate}

@@

\item
  Any objection to the qualification of any voter must be raised at
  the meeting at which the vote is tendered and the decision of the
  person who is chairing the meeting shall be final.
\item
  \begin{enumerate}
  \item
    Any organisation that is a member of the association may nominate any
    person to act as its representative at any meeting of the association.
  \item
    The organisation must give written notice to the association of the
    name of its representative. The representative shall not be
    entitled to represent the organisation at any meeting unless the
    notice has been received by the association. The representative may
    continue to represent the organisation until written notice to the
    contrary is received by the association.
  \item
    Any notice given to the association will be conclusive evidence that
    the representative is entitled to represent the organisation or
    that his or her authority has been revoked. The association shall not
    be required to consider whether the representative has been
    properly appointed by the organisation.
  \end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    A director must be a natural person aged 16 years or older.
    No one may be appointed a director if he or she would be
    disqualified from acting under the provisions of article
    \ref{director-cease}.
  \item
    The number of directors shall be not less than three, nor more than eight.

  \item
    The first directors shall be those persons notified to Companies
    House as the first directors of the association.

  \item
    A director may not appoint an alternate director or anyone to act
    on his or her behalf at meetings of the directors.
  \end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    The directors shall manage the business of the association and may
    exercise all the powers of the association unless they are subject to
    any restrictions imposed by the Companies Acts, the articles or any
    special resolution.
  \item
    No alteration of the articles or any special resolution shall have
    retrospective effect to invalidate any prior act of the directors.
  \item
    Any meeting of directors at which a quorum is present at the time
    the relevant decision is made may exercise all the powers
    exercisable by the directors.
  \end{enumerate}

@@

\item
  The association may by ordinary resolution:
  \begin{enumerate}
  \item
    appoint a person who is willing to act to be a director; and
  \item
    determine the rotation in which any additional directors are to
    retire.
  \end{enumerate}

\item
  No person other than a director retiring by rotation may be
  appointed a director at any general meeting unless:
  \begin{enumerate}
  \item
    he or she is recommended for re-election by the directors; or
  \item
    not less than fourteen nor more than thirty-five clear days before
    the date of the meeting, the association is given a notice that:
    \begin{enumerate}
    \item
      is signed by a member entitled to vote at the meeting;
    \item
      states the member's intention to propose the appointment of a
      person as a director;
    \item
      contains the details that, if the person were to be appointed, the
      association would have to file at Companies House; and
    \item
      is signed by the person who is to be proposed to show his or her
      willingness to be appointed.
    \end{enumerate}
  \end{enumerate}
\item
  All members who are entitled to receive notice of a general meeting
  must be given not less than seven nor more than twenty-eight clear
  days' notice of any resolution to be put to the meeting to appoint
  a director other than a director who is to retire by rotation.

\item
  \begin{enumerate}
  \item
    The directors may appoint a person who is willing to act to be a
    director.
  \item
    A director appointed by a resolution of the other directors must
    retire at the next annual general meeting and must not be taken
    into account in determining the directors who are to retire by
    rotation.
  \end{enumerate}
\item
  The appointment of a director, whether by the association in general
  meeting or by the other directors, must not cause the number of
  directors to exceed any number fixed as the maximum number of
  directors.

@@

\item \label{director-cease}
  A director shall cease to hold office if he or she:
  \begin{enumerate}
    \item
    ceases to be a director by virtue of any provision in the
    Companies Acts or is prohibited by law from being a director; 
    \item
    ceases to be a member of the association; 
    \item
    becomes incapable by reason of mental disorder, illness
    or injury of managing and administering his or her own affairs;
    \item 
    resigns as a director by notice to the association (but only if at
    least two directors will remain in office when the notice of
    resignation is to take effect); or 
    \item 
    is absent without the
    permission of the directors from all their meetings held within a
    period of six consecutive months and the directors resolve that his
    or her office be vacated.
  \end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    The directors may delegate any of their powers or functions to a
    committee of two or more directors but the terms of any delegation
    must be recorded in the minute book.
  \item
    The directors may impose conditions when delegating, including the
    conditions that:
    \begin{enumerate}
    \item
      the relevant powers are to be exercised exclusively by the
      committee to whom they delegate;
    \item
      no expenditure may be incurred on behalf of the association except in
      accordance with a budget previously agreed with the directors.
    \end{enumerate}
  \item
    The directors may revoke or alter a delegation.
  \item
    All acts and proceedings of any committees must be fully and
    promptly reported to the directors.
  \end{enumerate}

@@

\item \label{directors-interests}
  A director must declare the nature and extent of any interest,
  direct or indirect, which he or she has in a proposed transaction
  or arrangement with the association or in any transaction or
  arrangement entered into by the association which has not previously
  been declared. A director must absent himself or herself from any
  discussions of the directors in which it is possible that a
  conflict will arise between his or her duty to act solely in the
      interests of the association and any personal interest (including but
  not limited to any personal financial interest).

@@

\item
The directors must keep minutes of all:
    \begin{enumerate}
        \item
            appointments of officers made by the directors;
        \item
            proceedings at meetings of the association;
        \item
            meetings of the directors and committees of directors including:
            \begin{enumerate}
                \item
                    the names of the directors present at the meeting;
                \item
                    the decisions made at the meetings; and
                \item
                    where appropriate the reasons for the decisions.
            \end{enumerate}
    \end{enumerate}
